Testing production scenarios for (anti-)(hyper-)nuclei and exotica at LHC energies

### 2019-02-20 FrascatiPlot/Paper/aps/submit_20022019/main_aps.tex
Üpdate

\indent For the first time, LHC data allow for the study of \mbox{(anti-)(hyper-)nuclei} production as a function of the system- and object-size. 
A quantitative comparison of the production scenarios has been proposed in \cite{Mrowczynski:2016xqm}, resulting in the idea  to study the production rates of nuclei with similar mass but very different internal structure, as \hefour~and ${}^{4}\mathrm{Li}$ \cite{Bazak:2018hgl}. 
As ${}^{4}\mathrm{Li}$ is not stable with respect to strong decay, its measurement is experimentally difficult and probably less constraining than the systematic measurement of the (hyper-)nuclei coalescence parameters proposed here.

@@

In summary, under the assumption $R_1\approx R_2 \approx R_3 \approx R$ as in \cite{Blum:2017qnn} (see next section) and by combining Eq. 6.2 in \cite{Scheibl:1998tk} and our Eq.~\ref{eq:CA_general}, we obtain:
%
\begin{equation}
	\boxed {  B_{A} = {2J_{A} + 1 \over 2^{A}} {1 \over \sqrt{A}} {1 \over m_{T}^{A-1}} \Bigl({2\pi \over R^2 + ({r_A \over 2})^2 }\Bigr)^{3/2(A-1)} } \;.
\end{equation}
%
This general formula can be used to compare the predicted $B_{A}$ with data directly.

For small sources, as $R \rightarrow 0$, the coalescence probability is anti-proportional to the harmonic oscillator size parameter, and thus proportional to the depth of the attractive potential in the harmonic oscillator picture (and thus to the nucleus binding energy).
Quite naturally, the allowed momentum difference between the coalescing nucleons is larger for more attractive, i.e. deeper, potentials. 
For a large source, i.e. $R \gg r_A$, the coalescence probability is dominated by the classical phase-space separation, thus decreases for large distances in configuration space. 
%

>>>>

\indent For the first time, LHC data allow for the study of \mbox{(anti-)(hyper-)nuclei} production as a function of the system- and object-size. 
A quantitative comparison of the production scenarios has been proposed in \cite{Mrowczynski:2016xqm}, resulting in the idea  to study the production rates of nuclei with similar mass but very different internal structure, as \hefour~and ${}^{4}\mathrm{Li}$ \cite{Bazak:2018hgl}. 
As ${}^{4}\mathrm{Li}$ is not stable with respect to strong decay, its measurement is experimentally difficult and probably less constraining than the systematic measurement of the (hyper-)nuclei coalescence parameters propose d here.

@@

In summary, under the assumption $R_1\approx R_2 \approx R_3 \approx R$ as in \cite{Blum:2017qnn} and by combining Eq. 6.2 in \cite{Scheibl:1998tk} with our Eq.~\ref{eq:CA_general}, we obtain:
%
\begin{equation}
	\boxed {  B_{A} = {2J_{A} + 1 \over 2^{A}} {1 \over \sqrt{A}} {1 \over m_{T}^{A-1}} \Bigl({2\pi \over R^2 + ({r_A \over 2})^2 }\Bigr)^{3/2(A-1)} } \;.
\end{equation}
%
This general formula can be used to compare the predicted $B_{A}$ with data directly.

For small sources, as $R \rightarrow 0$, the coalescence probability is anti-proportional to the harmonic oscillator size parameter, and thus proportional to the depth of the attractive potential in the harmonic oscillator picture (and thus to the nucleus binding energy).
Quite naturally, the allowed momentum difference between the coalescing nucleons is larger for more attractive, i.e. deeper, potentials. 
For a large source where $R \gg r_A$, the coalescence probability is dominated by the classical phase-space separation, thus decreases for large distances in configuration space. 
%
